%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Jr. Software Engineer} % Job title
    {Saleswhale (YC S16)} % Organization
    {Singapore, Singapore} % Location
    {Nov. 2017 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item { Regularly delivered core product features and bug fixes for the main Saleswhale app with Rails, Ember.js, RSpec, Redis, Sidekiq. Contributed to product meetings and sign-offs.}
      \item { Empowered our Customer Success team in performing account onboarding, management, and health reporting by architecting and building an internal tool from scratch with Rails, Ember.js, Rspec, SemanticUI, Gulp. Took ownership of it and regularly updated it to support the internal operational requirements of our product roadmap and in response to user feedback}
      \item { Drastically reduced product testing times and accelerated feature releases by building and automating the deployment of a testing framework micro-service with Rails, AWS SQS, Docker, Fabric from scratch to mock the asynchronous operations of another bottleneck micro-service}
      \item { Took charge of engineering support tickets filed by other departments related to codebase that I am familiar with, and to investigate, prepare, and deploy a fix if necessary}
      \item { Helped the Operations team meet key SLAs by developing a Tableau workbook from scratch to return insights on operational metrics and performance }
      \item { In charge of the algorithms \& data structures segment of the technical interview for hiring new software engineers, and also helped to onboard new engineers to the codebase}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {SWAT} % Organization
    {Singapore, Singapore} % Location
    {Jan. 2017 - Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item { Helped to drive insights for the company's expansion strategy by finding pertinent datapoints via clustering large transport data}
      \item { Sought to find best clustering method to yield useful datapoints. Research report included details on data exploration and cleaning, data transformation, comparison of clustering algorithms (K-means, K- medoids, DBSCAN, Hierarchical clustering), and optimization of clustering parameters.}
      \item { Developed an end-to-end solution in R to perform the above.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Instructor} % Job title
    {Hwa Chong Institution} % Organization
    {Singapore, Singapore} % Location
    {Oct. - Dec. 2016, Oct - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item { Instructor of Hwa Chong Institution’s (HCI) Informatics Olympiad team}
      \item { Conducted weekly lectures and practice contests for around 20 students to prepare them for the National Olympiad in Informatics (NOI)}
      \item { Helped to achieve HCI's best ever performance in NOI in 2018, with 6 Golds and 3 Silvers from a team of 10. HCI was also ranked first in Junior College category}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Company Quartermaster Sergeant} % Job title
    {Singapore Armed Forces} % Organization
    {Singapore, Singapore} % Location
    {Jan. 2016 - Nov. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Commands and oversees the logistics division in ’J’ Company, Specialist Cadet School}
      \item {Ensure the requisition, accounting, maintenance, and distribution of supplies to troops}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
